full title

### 2020-11-21 paper/pldi21/eval-opaque.tex
Work in progress

\subsection{Opaque Function Coverage}
To evaluate how much manual modeling efforts of opaque functions
are reduced by dynamic shortcuts, we measured the number of tests where
opaque functions that are analyzed only by dynamic analysis not by
static analysis.  Table~\ref{table:func-replace} summarizes the result.
For 198 original tests and 143 abstracted tests, we measured the
number of tests that use only dynamic shortcuts instead of manual modeling
for each JavaScript built-in library function.  For each row,
\textbf{Object} column denotes a built-in object, \textbf{Function} a function
name, and \textbf{\# Replaced} the number of tests successfully replacing manual
modeling via dynamic shortcuts with the total number of tests using the target function.
For example, the first row in the left side describes that \jscode{Array} is used in
203 original tests and 116 abstracted tests.  Among them, 203 original
tests 90 abstracted tests are successfully analyzed by dynamic shortcuts
instead of using the modeling of \jscode{Array}.  Each filled cell describes
fully replaceable cases in Table~\ref{table:func-replace}.  Therefore, dynamic
shortcuts effectively lessen the burden of manual modeling for JavaScript
built-in functions.  Again, since all the original Lodash 4 tests except one
test is finisehd with a single dynamic shortcut, all the built-in fuctions
except \jscode{Math.floor} and \jscode{Function.prototype.call} are replaceable
for original tests.  For abstracted tests, 12 functions out of 60 built-in
functions are analyzed by only dynamic shortcut instead of manual modeling.

>>>>

\subsection{Opaque Function Coverage}
To evaluate how much manual modeling efforts of opaque functions
are reduced by dynamic shortcuts, we measured the number of tests where
opaque functions that are analyzed only by dynamic analysis not by
static analysis.  Table~\ref{table:func-replace} summarizes the result.
For 263 original tests and 167 abstracted tests, we measured the
number of tests that use only dynamic shortcuts instead of manual modeling
for each JavaScript built-in library function.  For each row,
\textbf{Object} column denotes a built-in object, \textbf{Function} a function
name, and \textbf{\#~Replaced} the number of tests successfully replacing manual
modeling via dynamic shortcuts over the total number of tests using the target function.
For example, the first row in the left side describes that \jscode{Array} is used in
203 original tests and 116 abstracted tests.  Among them, 203 original
tests and 90 abstracted tests are successfully analyzed by using dynamic shortcuts
instead of manual modeling of \jscode{Array}.  Each filled cell describes
a fully replaceable case.  Therefore, dynamic
shortcuts effectively lessen the burden of manual modeling for JavaScript
built-in functions.  Again, since all the original Lodash 4 tests except one
is finisehd with a single dynamic shortcut, all the built-in fuctions
except \jscode{Math.floor} and \njscode{Function.prototype.call} are replaceable
for original tests.  For abstracted tests, 12 functions out of 60 built-in
functions are analyzed by only dynamic shortcut instead of manual modeling.

### 2020-11-21 paper/pldi21/eval.tex
No highlighting for Function
Work in progress

We evaluate $\tool$ using the following research questions:
\begin{itemize}
\item \textbf{RQ1) Analysis Speed-up:} How much analysis time is reduced by
using dynamic shortcuts?
\item \textbf{RQ2) Precision Improvement:} How much analysis precision is
improved by using dynamic shortcuts?
% instead of manual modeling?
\item \textbf{RQ3) Opaque Function Coverage:} How many opaque functions are
covered only by dynamic shortcuts?
% without using manual modeling?
\end{itemize}
We selected the official 306 tests of Lodash 4
(v.4.17.20)\footnote{https://github.com/lodash/lodash/blob/4.17.20/test/test.js}
used in the examples in Section~\ref{sec:motivation} as our evaluation target.
Recent work~\cite{value-refinement,
value-partitioning} also used the tests to evaluate their techniques.
Among them, we filtered out 37 tests that use JavaScript language
features SAFE does not support such as dynamic code generation using
\jscode{Function}, getters and setters, and browser-specific features like $\jscode{__proto__}$.
Thus, we used 269 out of 306 tests for the evaluation of $\tool$.
We performed our experiments on a Ubuntu machine
equipped with 4.2GHz Quad-Core Intel Core i7 and 64GB of RAM.

@@

For abstracted tests as well, DS outperformed no-DS.
Figure~\ref{fig:abs-analysis-time} shows the analysis time of the abstracted tests.
Only four tests for no-DS and nine tests for DS are finished between 2 to 5 minutes.
Among 269 abstracted tests, no-DS finished analysis of 158 tests within 5 minutes,
but DS finished analysis of 168 tests.  For finished tests, the average analysis
time is 44.88 seconds for no-DS and 42.28 seconds for DS. Among 158 tests analyzed by no-DS, DS
timed-out for 15 tests.  For 143 tests analyzable by both analyzers,
DS outperformed no-DS up to 50.60$\x$ and 6.30$\x$ on average.

@@

\begin{table*}[t]
  \caption{Number of \textit{abstracted} tests using dynamic shortcuts
  instead of manual modeling for each JavaScript built-in library}
  \label{table:func-replace}
  \vspace*{-1em}
  \centering
  \scriptsize
  \[
\quad
    \begin{array}{c|l|c|c?c|l|c|c?c|l|c|c}

@@

      \mysutf{1}{}          {min  }      { 64 /  64}{ 15 /  48} & \mysutf{1}{Function}     {apply   }     {263 / 263}{124 / 167} & \mysutf{1}{}       {new RangeError}  {  0 /   0}{  0 /   3} \mylinefff

>>>>

We evaluate $\tool$ using the following research questions:
\begin{itemize}
\item \textbf{RQ1) Analysis Speed-up:} How much analysis time is reduced by
using dynamic shortcuts?
\item \textbf{RQ2) Precision Improvement:} How much analysis precision is
improved by using dynamic shortcuts?
% instead of manual modeling?
\item \textbf{RQ3) Opaque Function Coverage:} How many opaque functions are
covered only by dynamic shortcuts?
% without using manual modeling?
\end{itemize}
We selected the official 306 tests of Lodash 4
(v.4.17.20)\footnote{https://github.com/lodash/lodash/blob/4.17.20/test/test.js}
used in the examples in Section~\ref{sec:motivation} as our evaluation target.
Recent work~\cite{value-refinement,
value-partitioning} also used the tests to evaluate their techniques.
Among them, we filtered out 37 tests that use JavaScript language
features SAFE does not support such as dynamic code generation using
\njscode{Function}, getters and setters, and browser-specific features like $\jscode{__proto__}$.
Thus, we used 269 out of 306 tests for the evaluation of $\tool$.
We performed our experiments on a Ubuntu machine
equipped with 4.2GHz Quad-Core Intel Core i7 and 64GB of RAM.

@@

For abstracted tests as well, DS outperformed no-DS.
Figure~\ref{fig:abs-analysis-time} shows the analysis time of the abstracted tests.
Only four tests for no-DS and nine tests for DS are finished between 2 to 5 minutes.
Among 269 abstracted tests, no-DS finished analysis of 158 tests within 5 minutes,
but DS finished analysis of 167 tests.  For finished tests, the average analysis
time is 44.88 seconds for no-DS and 42.28 seconds for DS. Among 158 tests analyzed by no-DS, DS
timed-out for 15 tests.  For 143 tests analyzable by both analyzers,
DS outperformed no-DS up to 50.60$\x$ and 6.30$\x$ on average.

@@

\begin{table*}[t]
  \caption{Number of original and abstracted tests using dynamic shortcuts
only for each JavaScript built-in library}
  \label{table:func-replace}
  \vspace*{-1em}
  \centering
  \scriptsize
  \[
\quad
    \begin{array}{c|l|c|c?c|l|c|c?c|l|c|c}

@@

      \mysutf{1}{}          {min  }      { 64 /  64}{ 15 /  48} & \mnsutf{1}{Function}     {apply   }     {263 / 263}{124 / 167} & \mysutf{1}{}       {new RangeError}  {  0 /   0}{  0 /   3} \mylinefff
